A Comparison of R Tools for Nonlinear Least Squares Modeling

### 2024-02-08 JNABresubmission20231027/ComparingNLStools.Rmd
misc

```{r exhobbsfn, eval=TRUE}
hobnlfb<-nlfb(start=stu1, resfn=hobbs.res, jacfn=hobbs.jac)
pshort(hobnlfb) # use print(hobnlfb) for more detail
hobnlm<-nls.lm(par=stu1, fn=hobbs.res, jac=hobbs.jac)
pnlslm(hobnlm)  
hobgsln<-gsl_nls(start=stu1, fn=hobbs.res, y=rep(0,12))
pnls(hobgsln)
hobgsl<-gsl_nls(start=stu1, fn=hobbs.res, y=rep(0,12), jac=hobbs.jac)
pnls(hobgsl) # using analytic Jacobian
```

@@

```{r tetrarun}
time <- c( 1,  2,  3,  4,  6 , 8, 10, 12, 16)
conc <- c( 0.7, 1.2, 1.4, 1.4, 1.1, 0.8, 0.6, 0.5, 0.3)
NLSdata <- data.frame(time,conc)
NLSstart <- c(lrc1 = -2, lrc2 = 0.25, A1 = 150, A2 = 50) # a starting vector (named!)
NLSformula <- conc ~ A1 * exp(-exp(lrc1) * time) + A2 * exp(-exp(lrc2) * time)
tryit <- try(nls(NLSformula, data = NLSdata, start = NLSstart, trace = TRUE))
print(tryit)
```

>>>>

```{r exhobbsfn, eval=TRUE}
cat("hobnlfb<-nlfb(start=stu1, resfn=hobbs.res, jacfn=hobbs.jac)\n")
hobnlfb<-nlfb(start=stu1, resfn=hobbs.res, jacfn=hobbs.jac)
pshort(hobnlfb) # use print(hobnlfb) for more detail
cat("hobnlm<-nls.lm(par=stu1, fn=hobbs.res, jac=hobbs.jac)\n")
hobnlm<-nls.lm(par=stu1, fn=hobbs.res, jac=hobbs.jac)
pnlslm(hobnlm)  
cat("hobgsln<-gsl_nls(start=stu1, fn=hobbs.res, y=rep(0,12))\n")
hobgsln<-gsl_nls(start=stu1, fn=hobbs.res, y=rep(0,12))
pnls(hobgsln)
cat("hobgsl<-gsl_nls(start=stu1, fn=hobbs.res, y=rep(0,12), jac=hobbs.jac)\n")
hobgsl<-gsl_nls(start=stu1, fn=hobbs.res, y=rep(0,12), jac=hobbs.jac)
pnls(hobgsl) # using analytic Jacobian
```

@@

```{r tetrarun, echo=TRUE}
time <- c( 1,  2,  3,  4,  6 , 8, 10, 12, 16)
conc <- c( 0.7, 1.2, 1.4, 1.4, 1.1, 0.8, 0.6, 0.5, 0.3)
NLSdata <- data.frame(time,conc)
NLSstart <- c(lrc1 = -2, lrc2 = 0.25, A1 = 150, A2 = 50) # a starting vector (named!)
NLSformula <- conc ~ A1 * exp(-exp(lrc1) * time) + A2 * exp(-exp(lrc2) * time)
tryit <- try(nls(NLSformula, data = NLSdata, start = NLSstart, trace = TRUE))
print(tryit)
```
